---
title: "Laura's Capstone Project"
author: "Laura Daniel"
date: "8/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library("tm")) # for text minning
suppressMessages(library("SnowballC")) # for text stemming
suppressMessages(library("wordcloud")) # word-clud generation
suppressMessages(library("RColorBrewer")) # color palettes
```

## Overview

Throughout John's Hopkins Data Specialization course I have learned many things. I learned how to write R code and functions. I also learned a lot about how to perform statitics in R and how to strucutre data. The course also taught me several different ways to display the data and present it to the world. For this final capstone project in R, I will bring everything together and apply it to natural language processing. 

### About the Data
The corpora are collected from publicly available sources by a web crawler. Each entry is tagged with the type of entry, based on the type of website where it was collected.

**Read in files**
```{r read_data, cache=TRUE}
setwd("Desktop/Data_Specialization/R Programming/capstone/final/")
## reading in full data
blog<- readLines("en_US/en_US.blogs.txt", skipNul = TRUE)
news<- readLines("en_US/en_US.news.txt", skipNul=TRUE)
twitter <- readLines("en_US/en_US.twitter.txt", skipNul = TRUE)

## Reading in part of the data - will use this to work with.

b<- readLines("en_US/en_US.blogs.txt", n=1000, skipNul = TRUE)
n<- readLines("en_US/en_US.news.txt", n=1000, skipNul=TRUE)
t <- readLines("en_US/en_US.twitter.txt", n=1000, skipNul = TRUE)

combined <- c(b, n, t)
docs <- Corpus(VectorSource(combined))
```
 ** Task 1**
 *Transform, tokenize, and remove words*

```{r}
## when going back use
## Transforming Document
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
docs <- tm_map(docs, toSpace, "/")
docs <- tm_map(docs, toSpace, "@")
docs <- tm_map(docs, toSpace, "\\")
docs <- tm_map(docs, toSpace, "\-")
docs <- tm_map(docs, toSpace, "\\|")
docs <- tm_map(docs, toSpace, "\"")
docs <- tm_map(docs, toSpace, "\—")
docs <- tm_map(docs, toSpace, "\'")
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeNumbers)
docs <- tm_map(docs, removeWords, stopwords("english"))
docs <- tm_map(docs, removePunctuation)
docs <- tm_map(docs, stripWhitespace)
docs <- tm_map(docs, removeWords, c("fuck", "shit")) 
docs <- tm_map(docs, stemDocument)

token <- Boost_tokenizer(docs) #save this for latter
```
 

#### *Quiz 1*
```{}
max(nchar(news))
max(nchar(blog))
max(nchar(twitter))
 
love=length(grep("love", twitter))
hate=length(grep("hate", twitter))
love/hate 

biostat <- grep("biostats", twitter)
grep("A computer once beat me at chess, but it was no match for me at kickboxing", twit)
```

**Task 2**
Peform explority analysis and understand frequency of word and word pairs

A *term-document matrix* is a table containing the frequency of the words. Column names are words and row names are documents. 

```{r}
dtm <- TermDocumentMatrix(docs)
m <- as.matrix(dtm)
v <- sort(rowSums(m), decreasing = T)
d <- data.frame(word=names(v), freq=v)
head(d,10)
dim(d)
sum(d$freq[1:300]) ## approximately 300 words covers 90% of total words used
```

**Generate Word cloud**
```{r, fig.height=5}
set.seed(1234)
par(mar=c(1,1,1,1))
wordcloud(words = d$word, freq = d$freq, min.freq = 3,
          max.words=70, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))
```

```{r}
findFreqTerms(dtm, lowfreq = 51)
```
Table: Words that have frequencies >50

*What are the frequencies of 2-grams and 3-grams in the dataset?*
```{r}

```


## Helpful links
https://en.wikibooks.org/wiki/R_Programming/Text_Processing

*wordcloud*
http://www.sthda.com/english/wiki/text-mining-and-word-cloud-fundamentals-in-r-5-simple-steps-you-should-know